PANCHANGE_analysis

### 2020-10-09 PANCHANGE_analysis.Rmd
Regressions for OCI-R sensitivity analyses have also been added (although these will likely just be archived since we aren't including the OCI in this paper)

>>>>

# OCIR retro
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0a_estimates)
ocir_retro_model0a_estimates

# Regression diagnostic statistics
ocir_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0a_reg_stats)
ocir_retro_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0b_estimates)
ocir_retro_model0b_estimates

# Regression diagnostic statistics
ocir_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0b_reg_stats)
ocir_retro_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_estimates)
ocir_retro_model1a_estimates

# Regression diagnostic statistics
ocir_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_reg_stats)
ocir_retro_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_estimates)
ocir_retro_model1b_estimates

# Regression diagnostic statistics
ocir_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_reg_stats)
ocir_retro_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0a_explan_estimates)
ocir_retro_model0a_explan_estimates

# Regression diagnostic statistics
ocir_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0a_explan_reg_stats)
ocir_retro_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0b_explan_estimates)
ocir_retro_model0b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model0b_explan_reg_stats)
ocir_retro_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_explan_estimates)
ocir_retro_model1a_explan_estimates

# Regression diagnostic statistics
ocir_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_explan_reg_stats)
ocir_retro_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_explan_reg_stats)
ocir_retro_model1b_explan_reg_stats
```
